---
title: "Dracula Themed Document"
author: "Your Name"
execute: 
  echo: true
# format:
#   html:
#     theme: ../dracula.scss
#     highlight-style: dracula
format:
  html:
    embed-resources: true
    theme: ../dracula.scss
    highlight-style: dracula
---

## Introduction

Welcome to the **Dracula Theme Demo**. This document showcases various elements styled with the custom Dracula theme for Quarto.

## Images

![Dracula Logo](https://draculatheme.com/images/hero/dracula-icon.svg){width=100}


## R plots

First, let's create a Dracula ggplot theme:

```{r}
library(ggplot2)

theme_dracula <- function() {
  theme_minimal(base_size = 12, base_family = "Helvetica") +
    theme(
      plot.background = element_rect(fill = "#22212c", color = NA),
      panel.background = element_rect(fill = "#282a36", color = NA),
      panel.grid.major = element_line(color = "#44475a"),
      panel.grid.minor = element_blank(),
      axis.title = element_text(color = "#f8f8f2"),
      axis.text = element_text(color = "#f8f8f2"),
      plot.title = element_text(color = "#bd93f9", size = 14, face = "bold"),
      plot.subtitle = element_text(color = "#f8f8f2"),
      legend.background = element_rect(fill = "#22212c", color = NA),
      legend.key = element_rect(fill = "#282a36", color = NA),
      legend.text = element_text(color = "#f8f8f2"),
      legend.title = element_text(color = "#f8f8f2")
    )
}
```

```{r}

ggplot(mtcars, aes(x = wt, y = mpg, color = factor(gear))) +
  geom_point(size = 3) +
  labs(
    title = "Fuel Efficiency by Weight",
    subtitle = "Dracula Themed Plot",
    x = "Weight (1000 lbs)",
    y = "Miles per Gallon",
    color = "Gears"
  ) +
  scale_color_manual(values = c("#ff79c6", "#8be9fd", "#50fa7b")) +
  theme_dracula()
```


## Emphasis

- *Italic text*
- **Bold text**
- ***Bold and italic text***

## Numbered lists

1. First item
2. Second item
3. Third item

## Blockquote

> This is a blockquote. It should be styled according to the theme's blockquote styling.

## Lists

### Unordered List

- Item one
- Item two
  - Sub-item
- Item three

### Ordered List

1. First item
2. Second item
   1. Sub-item
3. Third item

## Code Examples

### Inline Code

This is an example of inline code: `x = y + z`

## Tables

| Syntax      | Description |
|-------------|-------------|
| **Header**  | Title       |
| *Italic*    | Text        |

## Links

You can find more about the Dracula theme [here](https://draculatheme.com/).



## Math Equations

Inline math: $E = mc^2$

Display math:

$$
\int_{-\infty}^{\infty} e^{-x^2} dx = \sqrt{\pi}
$$

## Conclusion

This concludes the demo of the **Dracula Theme** in Quarto. Feel free to add more elements to test the theme further.


